\textbf{{\Large {Recurrent relation for branching coefficients of affine Lie algebras}}}

### 2009-12-08 AffineLieAlgebras/InformalNotes/article.tex
The definitions of the objects are added after the first introduction of the recurrent relation

Here we present the final recurrent relation for the anomalous branching coefficients \eqref{eq:21}. 
\begin{equation}
  \label{eq:1}
k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
\sum_{\gamma \in
\Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
+\gamma }^{\left( \mu \right) }\right)   
\end{equation}
The proof of the formula and definitions of $\mathfrak{a}_{\bot},\; W_{\bot},\; s(\gamma),\; \Gamma_{\mathfrak{a}\subset \mathfrak{g}}$ are in the following subsection.

In the next section we describe the algorithm for the computation of branching coefficients based upon this formula and then present some example and discuss physical meaning.
\begin{comment}
  Fix the relation so that the definitions are available for the reader.
\end{comment}
\subsection{Proof of the recurrent relation}
\label{sec:proof}

>>>>

We present the final recurrent relation for the anomalous branching coefficients \eqref{eq:21}. 
\begin{equation}
  \label{eq:1}
k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
  \sum_{\omega\in W_{\bot}\backslash W} \epsilon(\omega)\; {\rm dim}\left(L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}\right) \delta_{\xi-\gamma_0,\pi_{\mathfrak{a}}(\omega(\mu+\rho)-\rho)}+
\sum_{\gamma \in
\Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
+\gamma }^{\left( \mu \right) }\right)   
\end{equation}
Here $\mathfrak{a}_{\bot}$ is the subalgebra generated by the roots of $\mathfrak{g}$ orthogonal to the root system of $\mathfrak{a}$, $W_{\bot}$ is the corresponding Weyl group, $\Gamma_{\mathfrak{a}\subset \mathfrak{g}}$ is the set of weights in the expansion of the product $\prod_{\alpha\in \Delta^{+}\setminus \Delta^{+}_{\mathfrak{a}_{\bot}}}(1-e^{-\alpha})^{\mathrm{mult}(\alpha)-\mathrm{mult}_{\mathfrak{a}}(\alpha)}$ and $s(\gamma)$ is the coefficient of $e^{\gamma}$ in this expansion.
The proof of the formula and more formal definitions of $\mathfrak{a}_{\bot},\; W_{\bot},\; s(\gamma),\; \Gamma_{\mathfrak{a}\subset \mathfrak{g}}$ are in the following subsection.

In the next section we describe the algorithm for the computation of branching coefficients based upon this formula and then present some example and discuss physical meaning.

\subsection{Proof of the recurrent relation}
\label{sec:proof}
